```{r}
source("Rscripts/utils.R")
#library(devtools)
#devtools::install_github("mrvollger/mrvplot")
#library(mrvplot)
```

# redo the plot above, but facet on existence of hap_snvs and filtered to hap selective in one tissue
```{r}
bl_vs_t_dataset_filtered %>%
    filter(
        hap_diff_bl_p_adjust <= 0.05 | hap_diff_t_p_adjust <= 0.05,
        is_t_peak, is_bl_peak,
    ) %>%
    mutate(
        is_hap_sel_in_bl = hap_diff_bl_p_adjust <= 0.05,
        is_hap_sel_in_t = hap_diff_t_p_adjust <= 0.05,
        case = case_when(
            is_hap_sel_in_bl & is_hap_sel_in_t ~ "both",
            TRUE ~ "one",
        ),
        has_snv = case_when(
            n_hap_snv > 0 ~ "Het",
            TRUE ~ "Homo",
        ),
    ) %>%
    filter(source == "real") %>%
    ggplot(aes(x=hap_diff_bl, y=hap_diff_t)) +
    geom_smooth(method="lm", color="black", se=F, linewidth=0.25, linetype="dashed") +
    geom_hex(bins=100) + scale_fill_distiller("", palette = "Spectral") +
    stat_cor(size=1.5) +
    coord_fixed() +
    facet_grid(haplotype~has_snv) +
    my_grid()
my_ggsave("Figures/BL-vs-T-hap-diff-facet-hap-snvs.pdf", width=4, height=4)
```

# show in the dimond plot with HCSA and somatic SNVs, do both all and just the hap selective ones
```{r}
this_df = bl_vs_t_dataset_filtered %>%
    filter(source == "real")

this_df = bind_rows(
    list(
        All=this_df,
        HSCA=this_df %>% filter(hap_diff_t_p_adjust <= 0.05)
    ),
    .id="source"
) %>%
mutate(
    HSCA = case_when(
        hap_diff_t_p_adjust <= 0.05 ~ "Hap-selective",
        TRUE ~ "Not hap-selective"
    ),
    HCSA = factor(HSCA, levels=c("Not hap-selective", "Hap-selective"))
)

this_df %>%
    ggplot(aes(x=hap_diff_bl, y=hap_diff_t)) +
    geom_hex(bins=100) + 
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    geom_point(
        data = . %>% filter(snv_count > 0),
        aes(
            x=hap_diff_bl, y=hap_diff_t,
            color = HSCA,
            alpha = HSCA
        ),
        #color="darkred",
        shape=3,
        #alpha=0.25,
        size=0.1,
    ) +
    coord_fixed() +
    scale_alpha_manual(
        values=c("Hap-selective"=1, "Not hap-selective"=0.1),
        guide="none"
    ) +
    scale_color_manual(
        "Somatic SNV",
        values=c("Hap-selective"="darkred", "Not hap-selective"="darkblue"),
    ) +
    scale_x_continuous(
        "Haplotype difference in accessibility (BL)",
        limits=c(-1, 1),
        label=percent,
    ) +
    scale_y_continuous(
        "Haplotype difference in accessibility (T)",
        limits=c(-1, 1),
        label=percent,
    ) +
    facet_grid(.~source) +
    my_grid()
my_ggsave("Figures/BL-vs-T-hap-diff-somatic-highlight.pdf", width=5, height=2)
```

# above but, I wonder if we just show one dimension and filter only for those sites that are not HSCA in BL, basically a histograms
```{r}
this_df = bl_vs_t_dataset_filtered %>%
    filter(
        source == "real", 
        hap_diff_bl_p_adjust > 0.05, 
        hap_diff_t_p_adjust <= 0.05
    )

this_df %>%
    ggplot(aes(x=hap_diff_t, 
        fill=snv_count > 0,
        #color=snv_count > 0
    )) +
    geom_histogram(binwidth=0.05) +
    scale_fill_manual(
        "HSCA in T",
        values=c(`TRUE`="darkred", `FALSE`="darkblue"),
        labels=c(`TRUE`="Somatic SNV", `FALSE`="No Somatic SNV")
    ) +
    scale_x_continuous(
        "Haplotype difference in accessibility (T)",
        label=percent,
        limits=c(-1, 1),
    ) +
    my_grid() +
    theme(
        legend.position = "top",
    )
my_ggsave("Figures/BL-vs-T-hap-diff-somatic-highlight-hist.pdf", width=3, height=2)
```

## same but lets make this a volcano plot
```{r}
colnames(bl_vs_t_dataset_filtered)
p_threshold = 0.05
tdf = bl_vs_t_dataset_filtered %>%
    filter(
        #n_hap_snv == 0,
        source == "real",
        hap_diff_bl_p_adjust > 0.05,
    ) %>%
    mutate(
        diff = hap_diff_t,
        p_adjust = hap_diff_t_p_adjust,
        p_value = hap_diff_t_p_value,
    )

cor_p_threshold = max(tdf[p_adjust <= p_threshold & !is.na(p_value) & !is.na(p_adjust) ]$p_value)
print(cor_p_threshold)
y_lim = ceiling(max(max(-log10(tdf$p_value)), max(-log10(tdf$p_adjust)))) 
y_by = 1 
#if(y_lim > 10){
#    y_by = 2
#}
min(tdf$p_value)
min_p_value = 1e-15
paste("<",scientific_10(1e-10))

# 
custom_scientific_10 <- function(x) {
    labels = scientific_10(x)
    # modify just the last element
    idx = length(labels)
    new_val = parse(text=paste(labels[idx], "- 0"))
    print(new_val)
    labels[idx] = new_val 
    labels
}
custom_scientific_10(c(1,1e-10))

tdf %>%
    mutate(
        p_value=case_when(
            p_value < min_p_value ~ min_p_value,
            TRUE ~ p_value
        )
    ) %>%
    ggplot(aes(x=diff, y=p_value)) +
    geom_hex(bins=100) + scale_fill_distiller("", palette = "Spectral", trans="log10") +
    geom_hline(aes(yintercept=(p_threshold)), linetype="dashed", color="darkblue", linewidth=0.3)+
    geom_hline(aes(yintercept=(cor_p_threshold)), linetype="dashed", color="blue", linewidth=0.3)+
    # add the somatic snvs as points
    geom_point(
        data = . %>% filter(snv_count > 0),
        aes(
            alpha = p_adjust <= p_threshold,
            size = p_adjust <= p_threshold,
        ), 
        color="darkred",
        shape=3,
    ) + 
    scale_alpha_manual(
        "",
        values=c(`TRUE`=1, `FALSE`=0.2),
        labels=c(`TRUE`="Somatic SNV", `FALSE`="No Somatic SNV"),
        #guide="none"
    ) +
    scale_size_manual(
        values=c(`TRUE`=1, `FALSE`=0.01),
        labels=c(`TRUE`="Somatic SNV", `FALSE`="No Somatic SNV"),
        guide="none"
    ) +
    scale_x_continuous("Difference between paternal and maternal accessibility",
        labels=percent,
        limits=c(-max(abs(tdf$diff)), max(abs(tdf$diff)))   
    ) +
    scale_y_continuous(
        "",
        #glue("p-value   (n = {n})"), 
        #labels=comma,
        breaks=10**(-seq(0, y_lim, y_by)),
        minor_breaks=10**(-seq(0, y_lim, 0.1)),
        trans=reverselog_trans(10),
        labels=custom_scientific_10,
    ) + 
    my_grid()

my_ggsave("Figures/BL-vs-T-hap-diff-somatic-highlight-volcano.pdf", height=2, width=3)
```

# plot the density of the haplotype differences for BL and t
```{r}
cn_vs_diff_df = bl_vs_t_dataset_filtered %>%
    filter(source=="real") %>%
    #filter(is_bl_peak, is_t_peak) %>%
    filter(is_t_peak | is_bl_peak) %>%
    filter(grepl("CN|DEL", cn_call)) %>%
    filter(grepl("CN|DEL", cn_cross_call)) %>% 
    mutate(
        cn_call_int = case_when(
            cn_call == "DEL" ~ 0,
            cn_call == "CN1" ~ 1,
            cn_call == "CN2" ~ 2,
            cn_call == "CN3" ~ 3,
            cn_call == "CN4" ~ 4,
            cn_call == ">CN4" ~ 5,
            TRUE ~ NA_real_
        ),
        cn_cross_call_int = case_when(
            cn_cross_call == "DEL" ~ 0,
            cn_cross_call == "CN1" ~ 1,
            cn_cross_call == "CN2" ~ 2,
            cn_cross_call == "CN3" ~ 3,
            cn_cross_call == "CN4" ~ 4,
            cn_cross_call == ">CN4" ~ 5,
            TRUE ~ NA_real_
        ),
    ) %>%
    select(-source, cn_cross_call, cn_call) %>%
    mutate(
        is_h1 = case_when(
            grepl("haplotype1", chrom) ~ TRUE,
            grepl("haplotype2", chrom) ~ FALSE,
            TRUE ~ NA
        ),
        should_flip = (cn_call_int > cn_cross_call_int) & is_h1,
        # figure out which is the normal vs amplified haplotype
        normal_fire_cov = case_when(
            should_flip ~ t_fire_h2,
            !should_flip ~ t_fire_h1,
        ),
        normal_cov = case_when(
            should_flip ~ t_cov_h2,
            !should_flip ~ t_cov_h1,
        ),
        normal_hap_frac = normal_fire_cov/normal_cov,
        #
        abnormal_fire_cov = case_when(
            should_flip ~ t_fire_h1,
            !should_flip ~ t_fire_h2,
        ),
        abnormal_cov = case_when(
            should_flip ~ t_cov_h1,
            !should_flip ~ t_cov_h2,
        ),
        abnormal_hap_frac = abnormal_fire_cov/abnormal_cov,
        normal_cn_call = case_when(
            cn_call_int > cn_cross_call_int ~ cn_cross_call_int,
            TRUE ~ cn_call_int,
        ),
        abnormal_cn_call = case_when(
            cn_call_int > cn_cross_call_int ~ cn_call_int,
            TRUE ~ cn_cross_call_int,
        ),

    ) %>%
    select(
        -cn_call_int, -cn_cross_call_int,
    ) %>%
    mutate(
        hap_diff_t = abnormal_hap_frac - normal_hap_frac,
    ) %>%
    pivot_longer(
        cols=c(hap_diff_bl, hap_diff_t),
        names_to="cell_type",
        values_to="hap_diff"
    ) %>%
    filter(
        !is.na(hap_diff),
    ) %>%
    mutate(
        cell_type = case_when(
            cell_type == "hap_diff_bl" ~ "BL",
            cell_type == "hap_diff_t" ~ "T",
            TRUE ~ NA_character_
        ),
    ) %>%
    select(-contains(c("n_somatic_snv."))) %>%
    data.table()    


cn_vs_diff_df %>%
    filter(
        normal_cn_call > abnormal_cn_call
    ) %>% nrow

cn_vs_diff_df %>%
    group_by(
        cell_type
    ) %>%
    summarise(
        t_peaks = sum(is_t_peak),
        bl_peaks = sum(is_bl_peak),
        has_amp = sum(abnormal_cn_call > normal_cn_call),
    )

```





# does the amount of template impact the fraction of accessible elements?
```{r}
# make a geom_hex like the others in this document of normal_hap_frac vs abnormal_hap_frac
normal_vs_amp_plot = cn_vs_diff_df %>%
    filter(cell_type=="T") %>%
    filter(is_t_peak) %>%
    ggplot(aes(x=normal_hap_frac, y=abnormal_hap_frac)) +
    geom_hex(bins=100) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor(size=2) +
    #geom_smooth(method="lm", color="darkred", se=F, linewidth=0.25, linetype="dashed") +
    geom_abline(slope=1, intercept=0, linetype="dashed", color="black", linewidth=0.5) +
    # add a geom point for significant points in T
    geom_point(
        data=. %>% filter(hap_diff_t_p_adjust <= 0.05 & F),
        color="darkred",
        alpha=0.5,
        size=0.1,
        # make the style a cross
        shape=3,
    ) +
    # make the aspect ratio 1:1
    coord_fixed() +
    scale_x_continuous(
        "Normal haplotype accessibility",
        label=percent,
        limits=c(0, 1),
    ) +
    scale_y_continuous(
        "Amplified haplotype accessibility",
        label=percent,
        limits=c(0, 1),
    ) +
    my_grid()

my_ggsave("Figures/BL-vs-T-norm-vs-amp-accessibility.pdf", width=2.5, height=2)
```

```{r}
# now do a similar plots, but show the fire coverage of the amplified haplotype divided by the normal haplotype on the Y axis and the amplified coverage divided by the normal coverage on the X axis

min_fires_for_analysis = MIN_COV

cn_vs_diff_looking_for_fire_diffs = cn_vs_diff_df %>%
    filter(is_t_peak) %>%
    filter(cell_type=="T") %>%
    filter(normal_fire_cov + abnormal_fire_cov > min_fires_for_analysis) %>%
    #filter(normal_hap_frac > 0.1 | abnormal_hap_frac > 0.1) %>%
    mutate(
        x = (abnormal_fire_cov+1)/(normal_fire_cov+1),
        y = (abnormal_cov+1)/(normal_cov+1),
    ) 

max_cn_ratio = 10

cn_vs_diff_looking_for_fire_diffs %>%
        mutate(
            x = case_when(
                x > max_cn_ratio ~ x,
                TRUE ~ x
            ),
            y = case_when(
                y > max_cn_ratio ~ y,
                TRUE ~ y
            )
    ) %>%
    mutate(
        hap_sel = case_when(
            hap_diff_t_p_adjust <= 0.05 ~ "Hap-selective",
            TRUE ~ "Not hap-selective"
        ),
    ) %>%
    ggplot(aes(x=x, y=y)) +
    geom_hex(
        #binwidth=0.1,
        bins=100,
    ) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor(
        data=cn_vs_diff_looking_for_fire_diffs,
        size=2
    ) +
    #geom_smooth(method="lm", color="darkred", se=F, linewidth=0.25, linetype="dashed") +
    geom_abline(
        slope=1, intercept=0, linetype="dashed", color="black", linewidth=0.5
    ) +
    # add a geom point for significant points in T
    geom_point(
        data=. %>% 
        filter(hap_diff_t_p_adjust <= 0.05),
        aes(x=x, y=y),
        color="darkred",
        alpha=0.5,
        size=0.1,
        # make the style a cross
        shape=3,
    ) +
    stat_regline_equation(
        data=cn_vs_diff_looking_for_fire_diffs,
        size=2, label.y=c(0.58)-0.03
    ) +
    # make the aspect ratio 1:1
    #coord_fixed() +
    scale_x_continuous(
        "Amplified hap coverage / CN normal hap coverage",
        trans="log10", label=comma,
        #limits=c(0, max_cn_ratio)
    ) +
    scale_y_continuous(
        "# FIREs amplified hap / # FIREs CN normal hap",
        trans="log10", label=comma,
        #limits=c(0, max_cn_ratio)
    ) + 
    coord_cartesian(
        #xlim=c(0, max_cn_ratio),
        #ylim=c(0, max_cn_ratio)
    ) +
    annotation_logticks(sides="bl") +
    my_grid()
my_ggsave("Figures/BL-vs-T-norm-vs-amp-accessibility-coverage.pdf", width=2.5, height=2)
```


# facet on CN state
```{r}
normal_vs_amp_plot = cn_vs_diff_df %>%
    filter(is_t_peak) %>%
    filter(cell_type=="T") %>%
    filter(
        #grepl("CN", normal_cn_call),
        #grepl("CN", abnormal_cn_call),
        normal_cn_call > 0,
        abnormal_cn_call > 0,
        !is.na(normal_cn_call),
        !is.na(abnormal_cn_call),
    ) %>%
    ggplot(aes(x=normal_hap_frac, y=abnormal_hap_frac)) +
    geom_hex(bins=100) +
    scale_fill_distiller("", palette = "Spectral", trans="log10") +
    stat_cor(size=2) +
    #geom_smooth(method="lm", color="darkred", se=F, linewidth=0.25, linetype="dashed") +
    geom_abline(slope=1, intercept=0, linetype="dashed", color="black", linewidth=0.5) +
    # add a geom point for significant points in T
    geom_point(
        data=. %>% filter(hap_diff_t_p_adjust <= 0.05 & F),
        color="darkred",
        alpha=0.5,
        size=0.1,
        # make the style a cross
        shape=3,
    ) +
    # make the aspect ratio 1:1
    coord_fixed() +
    scale_x_continuous(
        "Normal haplotype accessibility",
        label=percent,
        limits=c(0, 1),
    ) +
    scale_y_continuous(
        "Amplified haplotype accessibility",
        label=percent,
        limits=c(0, 1),
    ) +
    my_grid()+
    facet_grid(
        abnormal_cn_call ~ normal_cn_call
    ) 
my_ggsave("Figures/BL-vs-T-norm-vs-amp-accessibility-facet-cn.pdf", width=3, height=5)    

```






#
# somatic snv things
#


# regions very selective to hap 2 in T with little in BL
```{r}
bl_vs_t_dataset %>%
    filter(
        abs(hap_diff_bl) < 0.15,
        hap_diff_t < -0.80,
    ) %>%
    filter(
        source=="real",
    ) %>%
    select(-source) %>%
    fwrite(
        "Tables/Hap2-selective-in-T-only.bed", sep="\t", row.names=F, quote=F
    )


bl_vs_t_dataset_filtered %>%
    filter(
        snv_count > 0,
        abs(hap_diff_t) > 0.5,
    ) %>%
    filter(
        source=="real",
    ) %>%
    select(-source) %>%
    fwrite(
        "Tables/Hap1-selective-in-T-only-seen-in-hap1-background.bed", sep="\t", row.names=F, quote=F
    )
```


# test the frequency of peaks interesecting with somatic SNVs
```{r}
tbl = table(bl_vs_t_dataset[,is_somatic_snv, source])
table(bl_vs_t_dataset$is_somatic_snv)
tbl
# shuffle is greater than real
fisher.test(tbl, alternative="greater") 

```

# test the impact of somatic SNVs on the haplotype differences
```{r}
bl_vs_t_dataset_filtered %>%
    filter(
        source=="real",
    ) %>%
    mutate(
        hap_diff_t = case_when(
            hap_diff_t < -0.25 ~ -0.25,
            hap_diff_t > 0.25 ~ 0.25,
            TRUE ~ hap_diff_t
        ),
        # make abs
        #hap_diff_t = abs(hap_diff_t),
    ) %>%
    ggplot(aes(x=hap_diff_t, color=is_somatic_snv)) +
    geom_step(
        aes(y=stat(density)),
        stat="bin",
        binwidth=0.01, 
        alpha=0.75,
        linewidth=0.25,
        direction = "mid",
    ) +
    # note the number in each color class
    geom_text_repel(
        data=. %>% group_by(is_somatic_snv) %>% summarise(n=n()),
        aes(
            label=comma(n), 
            x=0.0, y=0.1),
        size=1.5,
        color="black",
        direction="y",
        seed=42,
    ) +
    scale_color_manual(
        "",
        values=c(`TRUE`="darkblue", `FALSE`="darkred"),
        labels=c(`TRUE`="Somatic SNV", `FALSE`="No Somatic SNV")
    ) +
    scale_x_continuous(
        "Haplotype difference in accessibility (T)",
        label=percent,
    ) +
    my_grid() 
my_ggsave("Figures/BL-vs-T-hap-diff-somatic-snv.pdf", width=3, height=2)
```

# which ones are showing that difference
```{r}
bl_vs_t_dataset_filtered %>%
    filter(
        source=="real",
        abs(hap_diff_t) > 0.25,
    ) %>%
    # plot individually showing the BL difference vs the T difference
    ggplot(aes(x=hap_diff_bl, y=hap_diff_t, color=is_somatic_snv)) +
    geom_point(
        alpha=0.5,
        size=0.5
    ) +
    # make the aspect ratio 1:1
    coord_fixed() +
    scale_x_continuous(
        "Haplotype difference in accessibility (BL)",
        limits=c(-1, 1),
    ) +
    facet_grid(.~is_somatic_snv) +
    scale_y_continuous(
        "Haplotype difference in accessibility (T)",
        limits =c(-1,1)
    ) +
    scale_color_manual(
        "",
        values=c(`TRUE`="darkblue", `FALSE`="darkred"),
        labels=c(`TRUE`="Somatic SNV", `FALSE`="No Somatic SNV")
    ) +
    my_grid() +
    theme(
        legend.position = "top",
    )
my_ggsave("Figures/BL-vs-T-hap-diff-somatic-snv-individual.pdf", width=3, height=2)
```







#
#
#
# UNUSED
#
#
#
```{r}
binwidth = 0.01
limit=0.25
#table(bl_vs_t_dataset_filtered[, other_hap_is_normal_cn, source])
p = cn_vs_diff_df %>%
    filter(is_bl_peak, is_t_peak) %>%
    mutate(
        hap_diff = case_when(
            hap_diff < -limit ~ -limit,
            hap_diff > limit ~ limit,
            TRUE ~ hap_diff
        )
    ) %>%
    ggplot(aes(x=hap_diff, color=cell_type, fill=cell_type)) +
    geom_step(
        aes(y=stat(density)),
        stat="bin",
        binwidth=binwidth, 
        alpha=0.75,
        linewidth=0.25,
        direction = "mid",
    ) +
   scale_color_manual(
        "",
        values=c("BL"="darkblue", "T"="darkred"),
    ) +
    scale_x_continuous(
        "Haplotype difference in accessibility",
        label=percent,
    ) +
    my_grid() +
    theme(

    )
my_ggsave("Figures/BL-vs-T-hap-diff-density.pdf", width=3, height=2)
p + facet_wrap(~cn_call, scales="free_y") +
    # add counts for each color class
    geom_text(
        data=. %>% filter(cell_type=="BL") %>% group_by(cn_call, cell_type) %>% summarise(n=n()),
        aes(
            label=comma(n),
            x=0.0, y=0.0,
            color=NULL
        ),
            color="black",
            size=1.5,
            vjust=0,
            #direction="y",
            #seed=42,
    ) 
my_ggsave("Figures/BL-vs-T-hap-diff-density-facet.pdf", width=4, height=2)
```


```{r}
bl_vs_t_dataset %>% 
    filter(source=="real") %>%
    filter(!is.na(t_cov) & !is.na(bl_cov)) %>%
    summarise(median(bl_cov), median(t_cov))


sim_of_peaks = bl_peaks %>%
    filter(
        coverage_H1 > MIN_COV, 
        coverage_H2 > MIN_COV,
    ) %>%
    sample_n(250e3) %>%
    rowwise() %>%
    mutate(
        frac_H1=fire_coverage_H1/coverage_H1,
        frac_H2=fire_coverage_H2/coverage_H2,
        sample_frac_H1 = mean(sample(
            c(
                rep(1, fire_coverage_H1),
                rep(0,coverage_H1-fire_coverage_H1)
            ),
            coverage_H1*124/303
        )),
        sample_frac_H2 = mean(sample(
            c(
                rep(1, fire_coverage_H2),
                rep(0,coverage_H2-fire_coverage_H2)
            ),
            coverage_H2*124/303
        ))
    ) %>%
    filter(
        (sample_frac_H1 + sample_frac_H2)/2 > LOD,
    ) %>%
    select(frac_H1, frac_H2, sample_frac_H1, sample_frac_H2) %>%
    mutate(
        diff = frac_H1 - frac_H2,
        sample_diff = sample_frac_H1 - sample_frac_H2
    ) %>%
    data.table


# pivot longer and the plot the distribution of the differences using ggplot and geom_step

sim_of_peaks %>%
    pivot_longer(
        cols=c(sample_diff, diff),
        names_to="type",
        values_to="value"
    ) %>%
    mutate(
        value = case_when(
            value < -limit ~ -limit,
            value > limit ~ limit,
            TRUE ~ value
        )
    ) %>%
    ggplot(aes(x=value, color=type)) +
    geom_step(
        aes(y=stat(density)),
        stat="bin",
        binwidth=0.01, 
        alpha=0.75,
        linewidth=0.25,
        direction = "mid",
    ) +
    scale_color_manual(
        "",
        values=c("diff"="darkblue", "sample_diff"="darkred"),
    ) +
    scale_x_continuous(
        "Haplotype difference in accessibility",
        limits=c(-limit, limit),
        label=percent,
    ) +
    my_grid()
my_ggsave("Figures/BL-vs-T-simulated-peaks-accessibility.pdf", width=3, height=2)
```



# plot the coverages of the different CN classes
```{r}
bind_rows(
    list(
        #all=bl_vs_t_dataset
        filtered=bl_vs_t_dataset_filtered
    ),
    .id="id"
) %>%
    filter(
        source=="real",
    ) %>%
    mutate(
        primary_t_coverage = case_when(
            grepl("haplotype1", chrom) ~ t_cov_h1,
            grepl("haplotype2", chrom) ~ t_cov_h2,
            TRUE ~ NA
        ),
        primary_t_coverage = case_when(
            primary_t_coverage > 250 ~ 250,
            TRUE ~ primary_t_coverage
        ),
    ) %>%
    ggplot(aes(x=primary_t_coverage, color=cn_call)) +
    geom_histogram(
        #aes(y=after_stat(density)),
        binwidth=1, alpha=0.5
    ) +
    geom_vline(
        xintercept=c(MIN_COV, 61.5),
        linetype="dashed",
        color="darkred",
    ) +
    scale_x_continuous(
        limit=c(-1, NA),
    ) +
    facet_grid(cn_call~id, scales="free") +
    my_grid() +
    # turn off clipping
    theme()
my_ggsave("Figures/BL-vs-T-t-coverage.pdf", width=5, height=4)
```



# just plot the accessibility of the normal vs amplified haplotype
```{r}
cn_vs_diff_df %>%
    filter(
        is_bl_peak, is_t_peak,
    ) %>%
    filter(grepl("CN|DEL", cn_call)) %>%
    filter(
        # remove cp 1 when in the T cell type
        !(cell_type == "T" & cn_call == "CN1"),
    ) %>%
    filter(
        !is.na(hap_diff),
    ) %>%
    mutate(
        hap_diff = case_when(
            hap_diff < -limit ~ -limit,
            hap_diff > limit ~ limit,
            TRUE ~ hap_diff
        )
    ) %>%
    ggplot(aes(x=normal_hap_frac, y=abnormal_hap_frac)) +
    geom_hex(bins=100) +
    scale_fill_distiller("", palette = "Spectral", trans="log10")+
    stat_cor(size=1.5) +
    geom_smooth(method="lm", color="darkred", se=F, linewidth=0.25, linetype="dashed") +
    geom_abline(slope=1, intercept=0, linetype="dashed", color="black", linewidth=0.25) +
    # make the aspect ratio 1:1
    coord_fixed() +
    scale_x_continuous(
        "Normal haplotype accessibility",
        limits=c(0, 1),
        label=percent,
    ) +
    scale_y_continuous(
        "Amplified haplotype accessibility",
        limits=c(0, 1),
        label=percent,
    ) +
    scale_color_manual(
        "",
        values=c("BL"="darkblue", "T"="darkred"),
    ) +
    facet_grid(
        .~cell_type, 
    ) +
    my_grid()
my_ggsave("Figures/BL-vs-T-norm-vs-amp-diff-accessibility.pdf", width=3, height=2)
```
