```{r}
source("Rscripts/utils.R")
#library(mrvplot)
```

# where the hap-selective sites are
```{r}
unique_hap_selective_t = bl_vs_t_dataset_filtered %>%
    filter(
        hap_diff_t_p_adjust <= 0.05
    ) %>%
    filter(
        (hap_diff_bl_p_adjust <= 0.05) == FALSE
    ) 
unique_hap_selective_t

unique_hap_selective_t_no_somatic = unique_hap_selective_t %>%
    filter(n_somatic_snv == 0)
```

# figure out where copy number changes are
```{r}
cn_states = cn %>% 
    group_by(chrom,CN) %>%
    bed_merge(
        #max_dist=101e3
        #max_dist=100e3,
        max_dist=20e3,
    ) %>%
    # add a numeric group that increases when the CN column changes state
    ungroup() %>%
    arrange(chrom, start) %>%
    group_by(chrom) %>%
    mutate(
        cn_change = CN != lag(CN),
        cn_group = cumsum(replace_na(cn_change, FALSE)),
    )  %>%
    data.table

cn_changes = cn_states %>%
    filter(cn_change) %>%
    mutate(
        end = start + 1
    )    
cn_changes %>%
    sample_n(10)
```

# test proximity of hap selective sites in somatic to CN changes
```{r}
other_peaks = bl_vs_t_dataset_filtered %>% filter(hap_diff_t_p_adjust > 0.05 & is_t_peak)

tdf = bind_rows(
    unique_hap_selective_t_no_somatic %>% 
    filter(n_hap_snv == 0) %>%
    mutate(
        type="Hap-selective peaks\n(no somatic SNVs, HOM)"
    ),
    unique_hap_selective_t_no_somatic %>% 
    filter(n_hap_snv > 0) %>%
    mutate(
        type="Hap-selective peaks\n(no somatic SNVs, HET)"
    ),
    #unique_hap_selective_t %>% filter(n_somatic_snv > 0) %>% mutate(type="hap_selective_t_with_somatic"),
    other_peaks %>% mutate(type="Other peaks"),
    other_peaks %>% bed_shuffle(genome=fai, seed=42) %>% mutate(type="Random genomic intervals"),
    bl_vs_t_dataset_filtered %>% filter(is_bl_peak) %>% mutate(type="BL peaks"),
    bl_vs_t_dataset_filtered %>% filter(is_bl_peak & hap_diff_bl_p_adjust <= 0.05) %>% mutate(type="Hap-selective BL peaks")

) %>%
    select(chrom, start, end, type, hap_diff_t) %>% unique()

how_close_hsca_to_cn_changes = merge(
    tdf,
    tdf %>% bed_closest(cn_changes, suffix=c("", "_cn_change")),
    all.x=TRUE,
    by=c("chrom","start","end","type", "hap_diff_t")
) %>%
    mutate(
        dist_to_cn = abs(.dist),
        no_change_on_chrom = is.na(.dist)
    ) %>%
    replace_na(list(dist_to_cn=max(.$dist_to_cn+10e3, na.rm=TRUE)))

```

# plot as a cdf the distnace to nearest CN change for hap selective vs other peaks
```{r}
cur_colors = c(
    "Hap-selective peaks\n(no somatic SNVs, HOM)"="darkred",
    "Hap-selective peaks\n(no somatic SNVs, HET)"="red",
    "Other peaks"="darkblue",
    "BL peaks"="darkgreen",
    "Hap-selective BL peaks"="forestgreen",
    "Random genomic intervals"="darkgray"
)
table(how_close_hsca_to_cn_changes$type)
how_close_hsca_to_cn_changes %>%
    ggplot(aes(x=dist_to_cn+1, color=type)) +
    stat_ecdf(alpha=0.75) +
    scale_x_continuous(
        "Distance to nearest copy number change",
        label=comma,
        #trans="log10",
    ) +
    #annotation_logticks(sides="b") +
    scale_y_continuous(
        "Cumulative % of haplotype-selective peaks",
        label=percent
    ) +
    scale_color_manual(
        "",
        values=cur_colors
    ) +
    my_grid( )+
    theme(
        legend.position = "right",
    ) 
my_ggsave("Figures/CN-changes-vs-haplotype-accessibility-distance-to-closest.pdf", width=3, height=2)
```

# on the ECDF I want to measure the delta between the hap-selective no somatic peaks and the other peaks
```{r}
t_ecdf_df = how_close_hsca_to_cn_changes %>%
    filter(type %in% c(
        "Hap-selective peaks\n(no somatic SNVs, HOM)", 
        "Hap-selective peaks\n(no somatic SNVs, HET)",
        "Other peaks")) %>%
    group_by(type) %>%
    summarise(
        x = seq(0, 20e6, by=1e3),
        value = ecdf(dist_to_cn+1)(x)
    ) %>% 
    ungroup() 

    #pivot_wider(names_from=type, values_from=value) %>%
    #mutate(
    #    delta = `Hap-selective peaks\n(no somatic SNVs)` - `Other peaks`
    #)
ecdf_df=t_ecdf_df %>%
    filter(type!="Other peaks") %>%
    merge(
        t_ecdf_df %>% filter(type=="Other peaks") %>% select(x, other_value=value),
        by="x",
        all.x=TRUE
    ) %>%
    mutate(
        delta = value - other_value
    ) %>%
    data.table()

max_delta = ecdf_df %>%
    group_by(type) %>%
    filter(delta == max(delta, na.rm=TRUE)) 
max_delta_dist = max_delta$x[which.max(max_delta$delta)]
# now plot the delta
ecdf_df %>%
    ggplot(aes(x=x, y=delta, color=type)) +
    geom_line() +
    # label with the max delta 
    geom_label_repel(
        data=max_delta,
        aes(
            label=paste0("Max delta = ", round(delta*100,2), "% at ", x/1e6, " Mbp"),
        ),
        size=2,
        segment.color=cur_colors[max_delta$type],
        color="black",
        min.segment.length = 0,
        #nudge_x = 1e6,
        nudge_y = 0.02,
    ) +
    scale_color_manual(
        "",
        values=cur_colors
    ) +
    scale_x_continuous(
        "Distance to nearest copy number change",
        label=comma,
    ) +
    scale_y_continuous(
        "Difference in cumulative % of peaks\n(hap-selective - other)",
        label=percent,
    ) +
    my_grid() +
    theme()
my_ggsave("Figures/CN-changes-vs-haplotype-accessibility-distance-to-closest-delta.pdf", width=3, height=2)
```

# save a table with these peaks
```{r}
hsca_close_to_cn_change = how_close_hsca_to_cn_changes %>%
    filter(type == "Hap-selective peaks\n(no somatic SNVs, HOM)") %>%
    select(-type) %>%
    filter(dist_to_cn <= max_delta_dist) 

hsca_close_to_cn_change %>%
    rename(`#chrom`=chrom) %>%
    fwrite("Tables/hap-selective-peaks-near-cn-changes.bed", sep="\t", quote=FALSE, row.names=FALSE, col.names=TRUE)
# /mmfs1/gscratch/stergachislab/mhsohny/SMaHT/Improving_SomaticVariantCalling_through_DSA/mrvollger/SMaHT-DSA-figures/Tables/hap-selective-peaks-near-cn-changes.bed
```


# make a ideogram showing me where these hap selective sites are
```{r}
how_close_hsca_to_cn_changes %>%
    filter(type == "Hap-selective peaks\n(no somatic SNVs, HOM)") %>%
    # color by postive or negative distance diff
    mutate(
        color = case_when(
            hap_diff_t > 0 ~ "Hap 1 increase",
            TRUE ~ "Hap 2 increase"
        ),
        hap = case_when(
            grepl("haplotype1", chrom) ~ "Hap 1",
            grepl("haplotype2", chrom) ~ "Hap 2",
            TRUE ~ "Unknown"
        )
    ) %>% 
    # merge with fai to get chromosome lengths
    merge(
        fai %>% select(chrom, size),
        by="chrom",
        all.x=TRUE
    ) %>%
    # organize chrom facets by size
    mutate(
        chrom = factor(chrom, levels=fai$chrom[order(fai$size, decreasing=TRUE)])
    ) %>%
    arrange(chrom, start) %>%
    ggplot(aes(
        x=(start+end)/2/1e6,
        fill=color
    )) +
    geom_histogram(
        binwidth=1,
    ) +
    geom_segment(
        aes(y=0, yend=0, x=0, xend=size/1e6),
    ) +
    scale_fill_manual(
        "",
        values=c(
            "Hap 1 increase"="darkred",
            "Hap 2 increase"="darkblue"
        )
    ) +
    facet_nested(hap+chrom~., 
        space="free",
        #scales="free_x"
        switch="y"
    ) +
    scale_x_continuous(
        "Genomic position (Mbp)",
        label=comma,
    ) +
    scale_y_continuous(
        "Count of haplotype-selective peaks\n(no somatic SNVs, HOM)",
        expand=expansion(mult=c(0,0.1))
    ) +
    my_grid() +
    #ggtitle("fake") +
    theme(
        strip.background = element_rect(fill="lightgray"),
        strip.text = element_text(size=2),
        legend.position = "top",
    )
my_ggsave("Figures/CN-changes-vs-haplotype-accessibility-hap-selective-peaks-ideogram.pdf", width=10, height=16)
```

```{r}
# chrs = haplotype1−0000008 and haplotype1−0000026 are interesting I think, maybe also haplotype1−0000001
keep_chrs = list("haplotype1-0000008", "haplotype1-0000026", "haplotype1-0000001")
how_close_hsca_to_cn_changes %>%
    filter(type == "Hap-selective peaks\n(no somatic SNVs, HOM)") %>%
    filter(chrom %in% keep_chrs) %>%
    arrange(chrom, start) %>%
    group_by(chrom) %>%
    mutate(
        dist_to_cn_mbp = dist_to_cn/1e6,
        dist_to_next_hap_sel = lead(start) - end,
    ) %>%
    select(chrom, start, end, hap_diff_t, dist_to_cn_mbp, dist_to_next_hap_sel) %>%
    arrange(chrom, start) 
    #pull(chrom) %>% table
```