# load bl-vs-t first
```{r}
bl_vs_t_dataset = fread("Tables/BL-vs-T-dataset.tbl.gz", sep="\t", header=T)    
bl_vs_t_dataset_filtered = fread("Tables/BL-vs-T-dataset-filtered.tbl.gz", sep="\t", header=T)
```

Of the *** COLO829 SNVs, DNVs, and indels that localize to loci that retain both haplotypes, only *** overlap a regulatory element that is accessible on at least one of the two haplotypes in COLO829 cells, consistent with regulatory DNA having an overall reduced cancer mutation rate
```{r}
names(bl_vs_t_dataset_filtered)
a_df = bl_vs_t_dataset_filtered %>%
    filter(cn_call >= 1 & cn_cross_call >=1 ) %>%
    as.tibble


n_bp_in_re = sum(a_df$end - a_df$start)
n_snvs_in_re = sum(a_df$n_somatic_snv)

n_bp_in_genome = cn_joint %>%
    filter(CN >= 1 & CN_cross >= 1) %>%
    dplyr::summarise(n_bp = sum(end - start)) %>%
    pull(n_bp)

n_snvs_in_joint = cn_joint %>%
    filter(CN >= 1 & CN_cross >= 1) %>%
    bed_map(
        snv,
        n_snvs = n()
    ) %>%
    filter(!is.na(n_snvs)) %>%
    dplyr::summarise(n_snvs = sum(n_snvs)) %>% 
    pull(n_snvs)

n_snvs_in_re/n_bp_in_re
n_snvs_in_joint/n_bp_in_genome
chisq_test = chisq.test(
    matrix(c(n_snvs_in_re, n_bp_in_re - n_snvs_in_re,
                   n_snvs_in_joint, n_bp_in_genome - n_snvs_in_joint), nrow=2),
)
chisq_test
```

# However, only 3.93***% (11/280***/***) of these somatic variants were associated with a significant change in chromatin accessibility on the haplotype that contains the somatic variant, with 4*** showing a decrease in chromatin accessibility, and 6*** showing an increase in chromatin accessibility
```{r}
bl_vs_t_dataset_filtered %>%
    filter(cn_call >= 1 & cn_cross_call >=1 ) %>%
    filter(n_somatic_snv > 0 ) %>%
    group_by(
        hap_diff_t_p_adjust <= 0.05
    ) %>%
    summarise(
        n = n(),
        n_somatic_snv = sum(n_somatic_snv),
        hap_diff_increase = sum(hap_diff_t > 0),
        hap_diff_decrease = sum(hap_diff_t < 0)
    )

bl_vs_t_dataset_filtered %>%
    filter(cn_call >= 1 & cn_cross_call >=1 ) %>%
    filter(n_somatic_snv > 0 ) %>%
    filter(
        hap_diff_t_p_adjust <= 0.05
    ) %>%
    select(n_somatic_snv, hap_diff_t)
```

# make a table of the hap selective ones with variants
```{r}
bl_vs_t_dataset_filtered %>%
    filter(cn_call >= 1 & cn_cross_call >=1 ) %>%
    filter(n_somatic_snv > 0 ) %>%
    filter(hap_diff_t_p_adjust <= 0.05) %>%
    select(chrom, start, end, 
        starts_with(c("t_", "bl_", "hap_", "n_hap_snv", "n_somatic_snv"))
    ) %>%
    # rename to start with #
    rename(`#chrom`=chrom) %>%
    fwrite("Tables/hap-selective-peaks-with-somatic-variants.bed", sep="\t", quote=FALSE, row.names=FALSE, col.names=TRUE)
```


# However, COLO829 cells contained an additional *** haplotype-selective elements that could not be explained by these somatic variants or by imprinted loci or germline variants, suggesting that additional genetic or epigenetic features may be playing a dominant role in modulating the chromatin epigenome of COLO829 cells. 
```{r}
bl_vs_t_dataset_filtered %>%
    #filter(cn_call >= 1 & cn_cross_call >=1 ) %>%
    filter(n_somatic_snv == 0 ) %>%
    filter(
        hap_diff_t_p_adjust <= 0.05
    ) %>%
    group_by(
        hap_diff_bl_p_adjust <= 0.05
    ) %>%
    summarise(
        n = n(),
        hap_diff_increase = sum(hap_diff_t > 0),
        hap_diff_decrease = sum(hap_diff_t < 0)
    )
```